A Data-Driven Framework for Neural Field Modeling

### 2010-12-28 ltx/first_order_framework/LaTeX_Manuscript.tex
fixed typo in appendix 2
corrected observation noise covariance estimation in dara paper
added section on correlation analysis

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

@@

The mapping between the membrane voltage and the electrophysiological data, denoted by $\mathbf y_t$, is modelled using the observation function that incorporates sensors with a spatial extent by
\begin{equation}
    \label{eq:ObservationEquation}
	\mathbf{y}_t =
	\int_{\Omega}{
	    m\left(\mathbf{r}_n-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)
	\, d\mathbf{r}'} + 
	\boldsymbol{\varepsilon}_t, 
\end{equation}
where $m\left(\mathbf{r}_n-\mathbf{r}'\right)$ is the observation kernel, $\mathbf{r}_n$ defines the location of the electrodes in the field, $n=1,...,n_y$ indexes the sensors and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes a multivariate normal distribution with mean zero and covariance matrix $\boldsymbol{\Sigma}_{\varepsilon}$.

@@

	&+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + \mathbf{e}_t(\mathbf{r}). 

@@

Now we define the state disturbance as
\begin{equation}\label{eq:Wt} 
	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} ) \, d\mathbf{r}},
\end{equation}
which is a zero mean normally distributed white noise process with covariance (see \ref{App:ColoredNoise} for the derivation)
\begin{equation}
	\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top} \, d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}. 
\end{equation}
The observation equation of the reduced model is found by substituting equation~\ref{DefFieldDecomp} into equation~\ref{eq:ObservationEquation} giving
\begin{equation}\label{eq:ReducedObservationEquation}
	\mathbf{y}_t = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r'}\right) \mathbf{x}_t\, d\mathbf{r}'} + \boldsymbol{\varepsilon}_t. 
\end{equation}
The observation equation is linear and can be written in the more compact form
\begin{equation}\label{ObservationEquation} 
	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
\end{equation}
where each element of the observation matrix is 
\begin{equation}
	\mathbf{C}_{ij} \triangleq \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}') \, d\mathbf{r}'.
\end{equation}

@@

@@

\clearpage
\newpage
\begin{figure*}[!ht]
\begin{center}
\includegraphics{fig1.pdf} 
\end{center}
\caption{}
\label{fig:Figure1}
\end{figure*}
\clearpage
\newpage
\begin{figure*}[!ht]
\begin{center}
\includegraphics{fig2.pdf} 
\end{center}
\caption{}
\label{fig:Figure2}
\end{figure*}
\clearpage
\newpage
\begin{figure*}[!ht]
\begin{center}
\includegraphics{fig3.pdf}
\end{center}
\caption{} 
\label{fig:Figure3}
\end{figure*}
\clearpage
\newpage
\begin{figure*}[!ht]
\begin{center}
\includegraphics{fig4.pdf}
\end{center}
\caption{}
\label{fig:Figure4}
\end{figure*}
\clearpage
\newpage
\begin{figure*}[!ht] 
\begin{center}
\includegraphics{fig5.pdf}	
\end{center}
\caption{}
\label{fig:Figure5}
\end{figure*}
\clearpage
\newpage
\begin{figure*}[!ht]
\begin{center}
\includegraphics{fig6.pdf}
\end{center}
\caption{}
\label{fig:Figure6}
\end{figure*}
\clearpage
\newpage
\begin{figure*}[!ht]
\begin{center}
\includegraphics{fig7.pdf}
\end{center}
\caption{} 
\label{fig:Figure7}
\end{figure*}
\clearpage
\newpage
\begin{figure*}[!ht]
\begin{center}
\includegraphics{fig8.pdf} 
\end{center}
\caption{} 
\label{fig:Figure8}
\end{figure*}
\clearpage
\newpage
\begin{figure*}[!ht]
\begin{center}
\includegraphics{fig9.pdf}
\end{center}
\caption{}
\label{fig:Figure9}
\end{figure*}
\clearpage
\newpage
\begin{figure*}[!ht]
\begin{center}
\includegraphics{fig10.pdf}
\end{center}
\caption{}
\label{fig:Figure10}
\end{figure*}
\clearpage
\newpage
\begin{figure*}[!ht]
\begin{center}
\includegraphics{fig11.pdf}
\end{center}
\caption{}
\label{fig:Figure11}
\end{figure*}
\clearpage
\newpage
\begin{figure*}[!ht]
\begin{center}
\includegraphics{fig12.pdf}
\end{center}
\caption{}
\label{fig:Figure12}
\end{figure*}
\clearpage
\newpage
\begin{figure*}[!ht]
\begin{center}
\includegraphics{fig13.pdf}
\end{center}
\caption{}
\label{fig:SensorAndSource}
\end{figure*}
\clearpage
\newpage
\begin{figure*}[!ht]
\begin{center}
\includegraphics{fig14.pdf}
\end{center}
\caption{}
\label{fig:Ch3}
\end{figure*}
\clearpage
\newpage
\appendix
\section{Time Discretization of the Neural Field Model}
\label{App:Time Discretization} To form the integro-difference equation neural field model, a time discretization must be performed. To do this, we used a one-step Euler method, where equation~\ref{FinalFormContinuous} can be approximated by 
\begin{align}
	\label{Euler Approximation}\frac{v\left( \mathbf{r},t+T_s \right) - v\left( \mathbf{r},t\right)}{T_s} &=-\zeta v\left( \mathbf{r},t \right) \nonumber \\ 
&+ \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}. 
\end{align}
For clarity, we shall index time points in the discrete time form of the model using the subscript $t$ and the next time point as $t+1$. Rearranging equation~\ref{Euler Approximation}, we get 
\begin{equation}
	\label{Euler Approximation2} v_{t+1}\left( \mathbf{r}\right) = v_t\left( \mathbf{r}\right) -T_s \zeta v_t\left( \mathbf{r}\right) + T_s \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'}. 
\end{equation}
Now making simplifications, the discrete time form of the model is 
\begin{equation}
	\label{Discrete Time Model1}v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'}, 
\end{equation}
where $\xi = 1 - T_s \zeta$.

\section{Observation Kernel}\label{App:ObsKernelExperiment}
The Gaussian shape of the observation kernel was verified experimentally. This was achieved by moving a dipole across a recording electrode submerged in saline. A photograph through a microscope of the submerged electrodes can be seen in Fig.~\ref{fig:SensorAndSource}. The measurement sensor was the most central electrode of a $5\times5$ Utah array (Blackrock Microsystems) which had electrode spacing of 400~$\mu$m. The current source was a twisted wire electrode (Plastics One Inc.) with tip-tip spacing of 60~$\mu$m and tip diameter of 200~$\mu$m. The twisted wire electrode was moved in the saline solution using a 3 dimensional manipulator (Sutter Instrument Company, MPC-100) in increments of 200~$\mu$m. The twisted wire electrode and the Utah array were co-registered visually using the microscope.
The stimulation waveform for the current source consisted of a 40~Hz sine wave with a duration of 1~s. The recording from the central electrode in the array was used to estimate the shape of the sensor kernel. To extract the amplitude of the signal, the data was first band-pass filtered with a center frequency of 40~Hz. The envelope of the signal was found by computing the mean instantaneous amplitude over the 1~s stimulation duration by
\begin{equation}
	a = \frac{1}{T}\sum_n{\sqrt{(y_t-\mathcal{H}y_t^2})}
\end{equation}
where $\mathcal{H}$ denotes the Hilbert transform operator, $t$ indexes samples and $T$ is the total number of samples in the time series. Fig.~\ref{fig:Ch3} shows the mean amplitude of the recorded envelope versus the distance between the twisted wire electrode and the recording electrode. A Gaussian fitted to the amplitudes is also shown. The figure shows that a Gaussian is indeed a good model for the sensor kernel in the homogeneous solution.
\section{Inner Product of Two \emph{n}-Dimensional Gaussians}\label{App:InnerProdOfGaussians}
The derivation in this section was used for calculating the matrix $\mathbf \Gamma$ from equation~\ref{eq:DefGamma}. Consider two Gaussian basis functions
\begin{equation}\label{eq:n_dimensional_Gaussian1}
 \varphi_i(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_i^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol \mu_i})\right)
\end{equation}
and 
\begin{equation}\label{eq:n_dimensional_Gaussian2}
\varphi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_j^2} (\mathbf r-\boldsymbol \mu_j)^\top(\mathbf r-\boldsymbol \mu_j})\right).
\end{equation}

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace} 
\usepackage{color}

\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}}

@@

The mapping between the membrane voltage and the electrophysiological data, denoted by $\mathbf y_t$, is modelled using the observation function that incorporates sensors with a spatial extent by
\begin{equation}
    \label{eq:ObservationEquation}
	y_t(\mathbf{r}_n) =
	\int_{\Omega}{
	    m\left(\mathbf{r}_n-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)
	\, d\mathbf{r}'} + 
	\varepsilon_t(\mathbf{r}_n), 
\end{equation}
\dean{(dean: I added $(\mathbf{r}_n)$ to index the observations)}
where $m\left(\mathbf{r}_n-\mathbf{r}'\right)$ is the observation kernel, $\mathbf{r}_n$ defines the location of the electrodes in the field, $n=1,...,n_y$ indexes the sensors and $\varepsilon_t(\mathbf{r}_n) \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes a multivariate normal distribution with mean zero and covariance matrix $\boldsymbol{\Sigma}_{\varepsilon}$.

@@

	&+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_t + \mathbf{e}_t(\mathbf{r}). 

@@

Now we define the state disturbance as
\begin{equation}\label{eq:Wt} 
	\mathbf{e}_t \triangleq \boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} ) \, d\mathbf{r}},
\end{equation}
which is a zero mean normally distributed white noise process with covariance (see \ref{App:ColoredNoise} for the derivation)
\begin{equation}
	\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top} \, d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top}. 
\end{equation}
The observation equation of the reduced model is found by substituting equation~\ref{DefFieldDecomp} into equation~\ref{eq:ObservationEquation} giving
\begin{equation}\label{eq:ReducedObservationEquation}
	\mathbf{y}_t = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r'}\right) \mathbf{x}_t\, d\mathbf{r}'} + \boldsymbol{\varepsilon}_t. 
\end{equation}
\dean{Note, the sensor index $\mathbf{r}_n$ has been omitted to delineate to reduced model observations from the full model.} The observation equation is linear and can be written in the more compact form
\begin{equation}\label{ObservationEquation} 
	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
\end{equation}
where each element of the observation matrix is 
\begin{equation}
	\mathbf{C}_{ij} \triangleq \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}') \, d\mathbf{r}'.
\end{equation}

@@

\subsection{Estimation of Connectivity Kernel Support}
The support of the connectivity kernel can be inferred using spatial correlation analysis. The method presented in this paper is based on a similar published method, where the kernel support was estimated using correlation analysis for a linear system described by an IDE~\citep{Scerri2009}. To demonstrate the method for the neural field model, we first define the spatial cross-correlation function between consecutive observations as 
\begin{align}
	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[y_{t}\left(\mathbf{r}_n+\boldsymbol{\tau}\right)y_{t+1}\left(\mathbf{r}_n\right)\right] \\
	&= \mathbf{E}\left[\left(\int_{\Omega}{
	    m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)
	\, d\mathbf{r}'} + 
	\boldsymbol{\varepsilon}_t\right)\left(\int_{\Omega}{
	    m\left(\mathbf{r}_n-\mathbf{r}'\right)v_{t+1}\left(\mathbf{r}'\right)
	\, d\mathbf{r}'} + 
	\boldsymbol{\varepsilon}_{t+1}\right)\right] \\
	&= \mathbf{E}\left[\int_{\Omega}{
	    m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)
	\, d\mathbf{r}'}\int_{\Omega}{
	    m\left(\mathbf{r}_n-\mathbf{r}'\right)v_{t+1}\left(\mathbf{r}'\right)
	\, d\mathbf{r}'} \right]
\end{align}
where $\mathbf{E}[\cdot]$ is the expected value. Substituting in equation~\ref{DiscreteTimeModel}  for $v_{t+1}\left(\mathbf{r}\right)$, the cross-correlation function is
\begin{align}
	R_{y_{t},y_{t+1}}(\boldsymbol{\tau}) &= \mathbf{E}\left[\int_{\Omega} {m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right)\, d\mathbf{r}'}\int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right) \left(\xi v_t\left(\mathbf{r}\right) +T_s \int_\Omega { w\left(\mathbf{r},\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right)\, d\mathbf{r}'}+ e_t\left(\mathbf{r}\right)\right)\, d\mathbf{r}'} \right] \\	
	 &= \xi\mathbf{E}\left[\int_{\Omega} {m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right)	\, d\mathbf{r}'}\int_{\Omega}
{m\left(\mathbf{r}_n-\mathbf{r}'\right) v_t\left(\mathbf{r}\right) d\mathbf{r}'} \right] \nonumber \\
	&+ T_s\mathbf{E}\left[\int_{\Omega} {m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, d\mathbf{r}'}\int_{\Omega} {m\left(\mathbf{r}_n-\mathbf{r}'\right) \int_\Omega { w\left(\mathbf{r},\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right)\, d\mathbf{r}'}\, d\mathbf{r}'} \right] \nonumber \\
	&+ \mathbf{E}\left[ \int_{\Omega} { m\left(\mathbf{r}_n + \boldsymbol{\tau} - \mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \,d\mathbf{r}' }\int_{\Omega} { m\left(\mathbf{r}_n-\mathbf{r}'\right) e_t \left(\mathbf{r}\right)\, d\mathbf{r}' } \right]
	\label{eq:spatialxcorr}
\end{align}

The first term on the right hand side of equation~\ref{eq:spatialxcorr} is
\begin{equation}
	\xi\mathbf{E}\left[\int_{\Omega} {m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right)	\, d\mathbf{r}'}\int_{\Omega}
{m\left(\mathbf{r}_n-\mathbf{r}'\right) v_t\left(\mathbf{r}\right) d\mathbf{r}'} \right] = \xi R_{y_{t},y_{t}}(\mathbf{\tau}),
\end{equation}
which is the spatial autocorrelation of the observations scaled by the decay parameter $\xi$. DOES THIS GIVE US AN ESTIMATE OF THE FIELD DISTURBANCE COVARIANCE? NUMERICALLY IT SEEMS TO GIVE SOMETHING VERY CLOSE. DEPENDS ON THE BANDWIDTH OF M. The last term on the right hand side of equation~\ref{eq:spatialxcorr} equates to zero since the disturbance added to the field at time $t$ and assumed to be uncorrelated to the field at time $t$. The middle term is
\begin{equation}
	T_s\mathbf{E}\left[\int_{\Omega} {m\left(\mathbf{r}_n+\boldsymbol{\tau}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, d\mathbf{r}'}\int_{\Omega} {m\left(\mathbf{r}_n-\mathbf{r}'\right) \int_\Omega { w\left(\mathbf{r},\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right)\, d\mathbf{r}'}\, d\mathbf{r}'} \right] = T_s\mathbf{E}\left[y_t(\mathbf{r}_n+\boldsymbol{\tau})\int_{\Omega} {m\left(\mathbf{r}_n-\mathbf{r}'\right) g_t(\mathbf{r})\, d\mathbf{r}'} \right],
\end{equation}
where
\begin{equation}
	g_t\left( \mathbf{r} \right) = \int_\Omega {w\left( \mathbf{r},\mathbf{r}' \right)f\left( v_t\left( \mathbf{r}' \right) \right)\, d\mathbf{r}'}. 
\end{equation}
% Therefore we can write
% \begin{equation}
% 	R_{v_{t},v_{t+1}}(\mathbf{\tau}) = \xi R_{v_{t},v_{t}}(\mathbf{\tau}) + T_s R_{v_{t},g_{t}}(\mathbf{\tau})
% \end{equation}
% and
% \begin{equation}\label{eq:xcorr_firing_and_field}
% 	T_s R_{v_{t},g_{t}}(\mathbf{\tau}) = R_{v_{t},v_{t+1}}(\mathbf{\tau})-\xi R_{v_{t},v_{t}}(\mathbf{\tau}).
% \end{equation}
% The spatial cross-correlation function $R_{v_{t},g_{t}}(\mathbf{\tau})$ depends on the shape of the spatial mixing kernel $w\left( \mathbf{r},\mathbf{r}' \right)$. Furthermore, the sign (polarity) of $R_{v_{t},g_{t}}(\mathbf{\tau})$ will be the same as the $w\left( \mathbf{r},\mathbf{r}' \right)$ for a given spatial location since the sigmoid function $f\left( v_t\left( \mathbf{r}' \right) \right) > \mathbf{0}$. Therefore, the support of the kernel can be inferred given the cross-correlation function $R_{v_{t},g_{t}}(\mathbf{\tau})$. The right hand side of equation~\ref{eq:xcorr_firing_and_field} can be calculated from data if $\xi$ is known. However, since $\xi$ is a decay parameter, we know that $\xi \in (0,1)$. Also, if we assume that
% \begin{equation}
% 	\xi R_{v_{t},v_{t}}(\mathbf{\tau}) \gg T_s R_{v_{t},g_{t}}(\mathbf{\tau})
% \end{equation}
% and
% \begin{equation}
% 	R_{v_{t},g_{t}}(\mathbf{0}) > 0,
% \end{equation}
% which corresponds to local excitation, then we can guess $\xi$ by incrementally increasing it from zero and evaluating equation~\ref{eq:xcorr_firing_and_field} until $T_s R_{v_{t},g_{t}}(\mathbf{0}) < 0$. The value of $\xi$ before $T_s R_{v_{t},g_{t}}(\mathbf{0}) < 0$ will provide the approximation.

@@

% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig1.pdf} 
% \end{center}
% \caption{}
% \label{fig:Figure1}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig2.pdf} 
% \end{center}
% \caption{}
% \label{fig:Figure2}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig3.pdf}
% \end{center}
% \caption{} 
% \label{fig:Figure3}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig4.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure4}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht] 
% \begin{center}
% \includegraphics{fig5.pdf}	
% \end{center}
% \caption{}
% \label{fig:Figure5}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig6.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure6}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig7.pdf}
% \end{center}
% \caption{} 
% \label{fig:Figure7}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig8.pdf} 
% \end{center}
% \caption{} 
% \label{fig:Figure8}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig9.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure9}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig10.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure10}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig11.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure11}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig12.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure12}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig13.pdf}
% \end{center}
% \caption{}
% \label{fig:SensorAndSource}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig14.pdf}
% \end{center}
% \caption{}
% \label{fig:Ch3}
% \end{figure*}
\clearpage
\newpage
\appendix
\section{Time Discretization of the Neural Field Model}
\label{App:Time Discretization} To form the integro-difference equation neural field model, a time discretization must be performed. To do this, we used a one-step Euler method, where equation~\ref{FinalFormContinuous} can be approximated by 
\begin{align}
	\label{Euler Approximation}\frac{v\left( \mathbf{r},t+T_s \right) - v\left( \mathbf{r},t\right)}{T_s} &=-\zeta v\left( \mathbf{r},t \right) \nonumber \\ 
&+ \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}. 
\end{align}
For clarity, we shall index time points in the discrete time form of the model using the subscript $t$ and the next time point as $t+1$. Rearranging equation~\ref{Euler Approximation}, we get 
\begin{equation}
	\label{Euler Approximation2} v_{t+1}\left( \mathbf{r}\right) = v_t\left( \mathbf{r}\right) -T_s \zeta v_t\left( \mathbf{r}\right) + T_s \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'}. 
\end{equation}
Now making simplifications, the discrete time form of the model is 
\begin{equation}
	\label{Discrete Time Model1}v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'}, 
\end{equation}
where $\xi = 1 - T_s \zeta$.

\section{Observation Kernel}\label{App:ObsKernelExperiment}
The Gaussian shape of the observation kernel was verified experimentally. This was achieved by moving a dipole across a recording electrode submerged in saline. A photograph through a microscope of the submerged electrodes can be seen in Fig.~\ref{fig:SensorAndSource}. The measurement sensor was the most central electrode of a $5\times5$ Utah array (Blackrock Microsystems) which had electrode spacing of 400~$\mu$m. The current source was a twisted wire electrode (Plastics One Inc.) with tip-tip spacing of 60~$\mu$m and tip diameter of 200~$\mu$m. The twisted wire electrode was moved in the saline solution using a 3 dimensional manipulator (Sutter Instrument Company, MPC-100) in increments of 200~$\mu$m. The twisted wire electrode and the Utah array were co-registered visually using the microscope.
The stimulation waveform for the current source consisted of a 40~Hz sine wave with a duration of 1~s. The recording from the central electrode in the array was used to estimate the shape of the sensor kernel. To extract the amplitude of the signal, the data was first band-pass filtered with a center frequency of 40~Hz. The envelope of the signal was found by computing the mean instantaneous amplitude over the 1~s stimulation duration by
\begin{equation}
	a = \frac{1}{T}\sum_t{\sqrt{(y_t^2-\mathcal{H}y_t^2})}
\end{equation}
where $\mathcal{H}$ denotes the Hilbert transform operator, $t$ indexes samples and $T$ is the total number of samples in the time series. Fig.~\ref{fig:Ch3} shows the mean amplitude of the recorded envelope versus the distance between the twisted wire electrode and the recording electrode. A Gaussian fitted to the amplitudes is also shown. The figure shows that a Gaussian is indeed a good model for the sensor kernel in the homogeneous solution.
\section{Inner Product of Two \emph{n}-Dimensional Gaussians}\label{App:InnerProdOfGaussians}
The derivation in this section was used for calculating the matrix $\mathbf \Gamma$ from equation~\ref{eq:DefGamma}. Consider two Gaussian basis functions
\begin{equation}\label{eq:n_dimensional_Gaussian1}
 \varphi_i(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_i^2} (\mathbf r-\boldsymbol \mu_i)^\top(\mathbf r-\boldsymbol \mu_i})\right)
\end{equation}
and 
\begin{equation}\label{eq:n_dimensional_Gaussian2}
\varphi_j(\mathbf r)=\mathrm{exp}\left({-\frac{1}{\sigma_j^2} (\mathbf r-\boldsymbol \mu_j)^\top(\mathbf r-\boldsymbol \mu_j})\right).
\end{equation}
